Quantifying Stability and Change in Personal Culture Using Panel Data

### 2023-09-30 manuscript/manuscript.Rmd
fixed equation

We estimate these using a form of variance decomposition. First, to measure stable interpersonal differences, we calculate $V(D)$ according to the equation below.[^2] 
$$
V(D) = 1 - \frac{\sum_{i=1}^N \sum_{t=1}^T [y_{it} - (\hat{\beta}_0 + \hat{\alpha}_{0i} + (\hat{\beta}_1 + \hat{\alpha}_{1i}) \overline{\text{year}}_{it})]^2}{\sum_{i=1}^N \sum_{t=1}^T [y_{it} - \bar{y}_{it}]^2}
$$

>>>>

We estimate these using a form of variance decomposition. First, to measure stable interpersonal differences, we calculate $V(D)$ according to the equation below, where $\widetilde{year_i}$ is the midpoint of the observed years for each respondent for that particular item.[^2] 
$$
V(D) = 1 - \frac{\sum_{i=1}^N \sum_{t=1}^T [y_{it} - (\hat{\beta}_0 + \hat{\alpha}_{0i} + (\hat{\beta}_1 + \hat{\alpha}_{1i}) \widetilde{\text{year}}_{i})]^2}{\sum_{i=1}^N \sum_{t=1}^T [y_{it} - \bar{y}_{it}]^2}
$$

### 2023-09-30 manuscript/manuscript.tex
fixed equation

We estimate these using a form of variance decomposition. First, to
measure stable interpersonal differences, we calculate \(V(D)\)
according to the equation below.\footnote{We use the model estimate from
  the midpoint year, rather than the value at the first wave, because
  this is the best measure of ``baseline'' available under the
  assumption that the person does not change. The first wave measure
  alone contains an unknown amount of measurement error and transient
  fluctuations.} \[
V(D) = 1 - \frac{\sum_{i=1}^N \sum_{t=1}^T [y_{it} - (\hat{\beta}_0 + \hat{\alpha}_{0i} + (\hat{\beta}_1 + \hat{\alpha}_{1i}) \overline{\text{year}}_{it})]^2}{\sum_{i=1}^N \sum_{t=1}^T [y_{it} - \bar{y}_{it}]^2}
\]

>>>>

We estimate these using a form of variance decomposition. First, to
measure stable interpersonal differences, we calculate \(V(D)\)
according to the equation below, where \(\widetilde{year_i}\) is the
midpoint of the observed years for each respondent for that particular
item.\footnote{We use the model estimate from the midpoint year, rather
  than the value at the first wave, because this is the best measure of
  ``baseline'' available under the assumption that the person does not
  change. The first wave measure alone contains an unknown amount of
  measurement error and transient fluctuations.} \[
V(D) = 1 - \frac{\sum_{i=1}^N \sum_{t=1}^T [y_{it} - (\hat{\beta}_0 + \hat{\alpha}_{0i} + (\hat{\beta}_1 + \hat{\alpha}_{1i}) \widetilde{\text{year}}_{i})]^2}{\sum_{i=1}^N \sum_{t=1}^T [y_{it} - \bar{y}_{it}]^2}
\]
